Server-Side Probabilistic Programming

### 2018-11-03 abstract/paper.tex
language edited

A probabilistic model in \texttt{infergo} is an implementation
of the \texttt{Model} interface requiring a single method
\texttt{Observe} which accepts a vector (a Go \textit{slice}) of
floats, the parameters to infer, and returns a single float,
interpreted as unnormalized log-likelihood of the posterior
distribution. The implementation of the methods can be written
in virtually unrestricted Go and use any Go libraries.

@@

\begin{itemize}
	\item The Go parser and abstract syntax tree serializer are a
		part of the standard library. Reading, transforming, and
		writing Go source code is straightforward and effortless.
	\item Type inference (or \textit{type checking} as it is
		called in the Go ecosystem), also provided in the
		standard library, augments parsing and allows to
		selectively apply transformation-based automatic
		differentiation  based on static expression types. 
	\item Go compiles and runs fast. Fast compilation and
		execution speeds allow to use the same facility for both
		exploratory design of probabilistic models and for
		inference in production environment.
	\item Go offers efficient parallel execution as a
		first-class feature, via so-called \textit{goroutines}.
		Goroutines streamline implementation of sampling-based
		inference algorithms. Sample generators and consumers
		are run in parallel, communicating through channels. 
		Inference is easy to parallelize in order to exploit
		hardware multi-processing, and samples are retrieved
		lazily for postprocessing. 
\end{itemize}

>>>>

A probabilistic model in \texttt{infergo} is an implementation
of the \texttt{Model} interface requiring a single method
\texttt{Observe} which accepts a vector (a Go \textit{slice}) of
floats, the parameters to infer, and returns a single float,
interpreted as unnormalized log-likelihood of the posterior
distribution. Implementation of model methods can be written
in virtually unrestricted Go and use any Go libraries.

@@

\begin{itemize}
    \item The Go parser and abstract syntax tree serializer are
        a part of the standard library. Parsing, transforming,
        and generating Go source code is straightforward and
        effortless.
	\item Type inference (or \textit{type checking} as it is
		called in the Go ecosystem), also provided in the
		standard library, augments parsing and allows to
		selectively apply transformation-based automatic
		differentiation  based on static expression types. 
	\item Go compiles and runs fast. Fast compilation and
		execution speeds allow to use the same facility for both
		exploratory design of probabilistic models and for
		inference in production environment.
	\item Go offers efficient parallel execution as a
		first-class feature, via so-called \textit{goroutines}.
		Goroutines streamline implementation of sampling-based
		inference algorithms. Sample generators and consumers
		are run in parallel, communicating through channels. 
		Inference is easy to parallelize in order to exploit
		hardware multi-processing, and samples are retrieved
		lazily for postprocessing. 
\end{itemize}
